Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-24 papers/ms.tex
update ms
propagated updated rotation periods for RSG-5

fix bibliography

Color-absolute magnitude diagrams (CAMDs) of the candidate RSG-5 and
CH-2 members are shown in the upper row of Figure~\ref{fig:age}.  The
stars from the $\delta$~Lyr cluster are from
\citet{bouma_kep1627_2022}, and the field stars are from the Gaia EDR3
Catalog of Nearby Stars \citep{gaia_gcns_2021}.  To make these
diagrams, we imposed the data filtering criteria from
\citet[][Appendix B]{GaiaCollaboration2018}, which 
include binaries while omitting instrumental artifacts from for
instance low photometric signal to noise, or a small number of
visibility periods.  We then corrected for extinction using the
\citet{lallement_threedimensional_2018}
dust maps\footnote{\url{https://stilism.obspm.fr/}} and the extinction coefficients $k_X\equiv A_X/A_0$ from
\citet{GaiaCollaboration2018}, assuming that $A_0 = 3.1 E(B-V)$.  This
yielded a mean and standard deviation for the reddening of
$E(B-V)=0.036\pm0.002$ for RSG-5, and $E(B-V)=0.017\pm0.001$
for CH-2.  By way of comparison, in \citet{bouma_kep1627_2022} the
same query for the $\delta$~Lyr cluster yielded
$E(B-V)=0.032\pm0.006$.  Finally, for the plots we set the
color range to best visualize the region of maximal age information
content: the pre-main-sequence.

@@

Figure~\ref{fig:age} also shows that most RSG-5 and
CH-2 members overlap with the $\delta$~Lyr cluster, and that the groups are therefore
roughly the same age.  To quantify this, we use the method
introduced by \citet[][their Section~6.3]{gagne_mutau_2020}.  The
idea is to fit the pre-main-sequence loci of a set of
reference clusters, and to then model the locus of the target cluster
as a linear combination of these reference cluster loci.  For our
reference clusters, we used UCL, IC\,2602, and the Pleiades, with the
memberships reported by \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively.  We adopted ages of 16\,Myr for
UCL \citep{pecaut_star_2016}, 38\,Myr for IC\,2602\footnote{ Ages for
IC\,2602 vary from 40 to 46\,Myr based on lithium-depletion-boundary
(LDB) measurements \citep{dobbie_ic_2010,randich_gaiaeso_2018}, and
from 30 to 46\,Myr based on isochronal analyses
\citep{stauffer_rotational_1997,david_ages_2015,bossini_age_2019}.},
and 112\,Myr for the Pleiades \citep{dahm_2015}.  These assumptions
and the subsequent processing steps taken to exclude field stars and binaries
were identical to those
described in \citet{bouma_kep1627_2022}.  The mean and 
uncertainty of the resulting age posterior are $46^{+9}_{-7}$\,Myr for
RSG-5, and $36^{+10}_{-8}$\,Myr for CH-2.  For comparison, this
procedure yields an age for the $\delta$~Lyr cluster of
$38^{+6}_{-5}$\,Myr.  
The slightly older isochronal age of RSG-5 is
consistent with its location
relative to the $\delta$~Lyr cluster in
the upper left panel of Figure~\ref{fig:age}.

@@

We selected stars suitable for gyrochronology by requiring $\bpmrpo
\geq 0.5$ to focus on FGKM stars that experience magnetic braking.
For TESS, we also restricted our sample to $G<16$, to ensure the stars
are bright enough to extract usable light curves from the full-frame
images.  The magnitude cut corresponds to $\bpmrpo < 2.6$
($\sim$M3V) at the relevant distances.  These cuts gave 19 stars in
CH-2 and 42 stars in RSG-5.  We extracted light curves from the TESS
images using the \texttt{unpopular} package
\citep{hattorio_2021_cpm}, and regressed them against systematics with
its causal pixel model.  We measured rotation periods using
Lomb-Scargle periodograms and visually vetted the results using an
interactive program that allows us to switch between TESS Cycles,
select particular sectors, flag stars with multiple periods, and
correct half-period harmonics. For ZTF, we used the same color cut to
focus on FGKM stars, but restricted the sample to $13 < G < 18$ to
avoid the saturation limit on the bright end and ensure sufficient
photometric precision at the faint end. We followed the procedure
outlined in \citet{curtis_rup147_2020}: we downloaded $8'\times8'$
image cutouts, ran aperture photometry for the target and neighboring
stars identified with Gaia, and used them to define a systematics
correction to refine the target light curves.

The lower panels of Figure~\ref{fig:age} show the results.  In RSG-5,
36/42 stars have rotation periods faster than the Pleiades (86\%).
This numerator omits the two stars with periods $>$$12$\,days visible in
the lower-left panel of Figure~\ref{fig:age}.  The age interpretation
for these latter stars, particularly the $\approx$M2.5 dwarf, is not
obvious.  \citet{rebull_usco_2018} for instance have found numerous
M-dwarfs with 10-12 day rotation periods at ages of USco ($\sim$$8$\,Myr),
and some may still exist at ages of LCC ($\sim$$16$\,Myr;
L.~Rebull in preparation).  Regardless, given that nearly no field
star outliers seem to be present on the RSG-5 CAMD, the fact that we
do not detect rotation periods for $\approx$14\% of stars should
perhaps be taken as an indication for the fraction of stars for
which rotation periods might not be detectable, due to {e.g.}, pole-on
stars having lower amplitude starspot modulation.

%
% CH-2
% 5 stars with Prot>10 days (from the Prot versus color plot):
%                      DESIGNATION  TESS_Data   bp_rp_x     period
%25  Gaia EDR3 2129930258400157440          4  1.909693  15.309000
%24  Gaia EDR3 2129417404945830784          4  2.040988  10.981582
%4   Gaia EDR3 2107169165113864064          4  2.059904  10.580494
%9   Gaia EDR3 2134851775526125696          4  2.326998  12.227900
%1   Gaia EDR3 2127726081184588160          4  2.347244  11.543281
%
% CH-2
% Photometric field stars (from Glue -- one of these is omitted due to phot S/N cut, 
% presumably 2126008609657702784 )
%
%In [9]: df[['DESIGNATION', 'bp_rp', 'M_G']]
%Out[9]:
%                     DESIGNATION     bp_rp        M_G
%0  Gaia EDR3 2126529468937923456  2.518077   9.844733 --> NaN period, G=16.9
%1  Gaia EDR3 2126008609657702784  2.746735  11.409737 --> NaN, G=18.4
%2  Gaia EDR3 2133330051428541952  2.499458   9.459546 --> 15.7 d (ZTF), G=16.5
%3  Gaia EDR3 2133510921093964928  2.720177  10.923209 --> NaN, G=17.9
%4  Gaia EDR3 2139369183468814464  2.929506  11.170221 --> NaN, G=18.2
%5  Gaia EDR3 2129930258400157440  1.909693   8.200652 --> P=15.3 (ZTF), G=15.2

@@

A few salient properties of the Kepler objects in Cep-Her can be
gleaned from Figure~\ref{fig:age}.  The stars span spectral types of
G8V (Kepler-1627) to K6V (KOI-7913 A).  The secondary in the KOI-7913
system has spectral type $\approx$K8V.  And given that a star with Solar mass
and metallicity arrives at the zero-age main sequence at
$t\approx40$ Myr \citep{choi_mesa_2016}, these stars are all in the
late stages of their pre-main-sequence contraction.  
% Their heliocentric distances are $\approx$260\,pc (KOI-7913 and
% KOI-7368, in CH-2) and $\approx$340\,pc (Kepler-1643, in RSG-5).

@@

We fitted the data as follows.  Given an initial guess for the transit
ephemeris from \citet{thompson_planetary_2018}, we first trimmed the
light curve to a local window around each transit that spanned three
transit durations before and after each mid-transit time.  The
out-of-transit points in each local window were then fitted with a
fourth-order polynomial, which was divided out from the light
curve.  The resulting flattened transits were then fitted with a
transit model that assumed quadratic limb darkening.
The model therefore included 8 free parameters for the transit ($\{P,
t_0, \log R_{\rm p}/R_\star, b, u_1 ,u_2, R_\star, \log g\}$), 2 free
parameters for the light curve normalization and a white noise jitter
($\{\langle f \rangle, \sigma_f \}$), and 5 fixed
parameters for each transit.

@@

One drawback of our approach is that we have fixed 5 implicit
parameters per individual transit to their MAP values to remove the
starspot-induced variability.  An alternative could be to fit the
planetary transits simultaneously with the starspot-induced
variability using a quasiperiodic Gaussian process (GP).  We
explored this approach, but found that it sometimes required fine-tuning
of the hyperparameter priors, otherwise the GP would 
overfit flares, instrumental noise, and any other variability that was not
part of the transit.  This failure mode is pernicious, in that it yields an
ill-founded sense of confidence in a visually clean
fit.  Our model is simpler, and it has the benefit that the white
noise jitter never trades off with any parameter equivalent to a
damping timescale for the coherence of the GP.  It is also
computationally efficient, and it captures the planetary parameters
about which we care the most.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
    Planets younger than a gigayear with ages more precise than a factor of
    three are emphasized. The Cep-Her planets are
    Kepler-1643~b ($\square$), KOI-7368~b ($\triangledown$),
    KOI-7913~Ab (X), and Kepler-1627~Ab (+).  
    Interesting trends in the population of young planets currently include
    {\it i)} their large sizes 
    and {\it ii)} the lack of young hot Jupiters.
    The new objects of interest in Cep-Her have normal mini-Neptune sizes
    between 2 and 3\,$R_\oplus$, which is a novelty given their ages.
    Parameters are from the NASA Exoplanet Archive (2022 Apr 5).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

The most significant novelty about
Kepler-1643~b, KOI-7368.01, and KOI-7913~Ab is that their sizes are
normal, relative to the known population of gigayear-old
mini-Neptunes.  At field star ages, mini-Neptune sizes span
1.8\,$R_\oplus$ to 3.6\,$R_\oplus$, with the most
common size being $\approx 2.4\,R_\oplus$
\citep[][Figure~7]{Fulton_et_al_2017}.  The known planets younger than
$10^8$ years are almost all larger, with sizes between 4 and
10$\,R_\oplus$
\citep{Mann_K2_33b_2016,David_et_al_2017,benatti_possibly_2019,david_four_2019,newton_tess_2019,rizzuto_tess_2020,bouma_cluster_2020,mann_toi1227_2022}.
Figure~\ref{fig:rp_period_age} explores this in more detail by showing
the sizes, orbital periods, and ages of the known transiting planets,
emphasizing planets with precise ages.  The smallest previously known planets
comparable to the new Cep-Her mini-Neptunes
are AU~Mic~c ($3.0\pm0.2\,R_\oplus$, see
\citealt{martioli_aumicbc_2021} and \citealt{gilbert_flares_2022}),
Kepler-1627~Ab ($3.8\pm0.2\,R_\oplus$; \citealt{bouma_kep1627_2022}),
and AU~Mic~d ($4.2\pm0.2\,R_\oplus$; \citealt{plavchan_planet_2020}).

The theoretical expectation is that mini-Neptunes with sizes of 2 to
3\,$R_\oplus$ should be common at ages of $10^7$ to $10^8$ years.
This expectation is tied to inferences about the
initial distributions of planetary core mass, core composition, and
atmospheric mass fraction \citep{owen_evaporation_2017}.  The
Kelvin-Helmholtz cooling timescale, which is tied to the entropy of
the planetary interior once the disk disperses, could also play a
significant role \citep{owen_constraining_2020}.  As an example,
\citet{rogers_unveiling_2021} predicted that given a core-mass
distribution peaked at $\approx$$4$\,$M_\oplus$, an ice-poor rock/iron
core composition, and a typical H/He mass fraction of $\approx$4\%,
there should be a maximum in planet occurrence at 2 to 3\,$R_\oplus$
at times between 10 and 100\,Myr
(their Figure~16).  The models advanced by
\citet{gupta_signatures_2020} and \citet{lee_primordial_2021} agree;
the theoretical differences lie in their explanations
for the radius valley.  If the radius gap is primordial
and created by gas accretion physics, then super-Earths
($<$$1.8$\,$R_\oplus$) would be common as early as $10^7$ years
\citep{lee_primordial_2021}.   The photoevaporation-driven models more
often quote $10^8$ year timescales for production of
atmosphere-stripped super-Earths, while the models with the mass-loss
driven by a slow escape of heat from the core predict longer
$\sim$$10^9$ year timescales (but see \citealt{king_euv_2020}).

@@

To quantify the density difference between CH-2 and RSG-5, we can compare the spatial and
velocity volumes searched for each group.
For RSG-5, we drew \nrsgfive\ candidate members from a $30\,{\rm
pc}\times30\,{\rm pc}\times30\,{\rm pc}$ spatial cube, given a $1 {\rm
\mkms} \times 2 {\rm \mkms }$ rectangle in apparent galactic velocity.
For CH-2, our \nchtwo\ candidate members came from a rectangular prism of
dimension $50\,{\rm pc}\times40\,{\rm pc}\times30\,{\rm pc}$, and a
rectangular box of $2 {\rm \mkms} \times 4 {\rm \mkms}$.  If we define
the searched volume in units of ${\rm pc}^3\,{\rm km^2}\,{\rm s^{-2}}$, then
the volume ratio of CH-2 to RSG-5 is 9 to 1.  The ratio of number
densities (candidate members per unit searched volume) in RSG-5
relative to CH-2 is 34 to 1.

Given its low density, in CH-2 really a star cluster?  For this
discussion, we adopt the definition that a star cluster is a group
of at least 12 stars that was physically associated at its time of
formation.  The somewhat arbitrary ``12'' is set to distinguish star
clusters from high-order multiples \citep[see][]{krumholz_star_2019}.
Dissolved clusters and their tidal tails are therefore included in our
concept of clusters.  We do not require however that a particular number of stars per
unit spatial volume is required for a group to be a ``cluster''.
The latter point acknowledges that an important
factor in cluster identification is also the density in velocity
space.  Perhaps once stellar rotation periods and chemical abundances
reach the same level of ubiquity as stellar proper motions, they might
enable further refinement of our ability to discover stars that formed
together.

From a data-driven perspective, demonstrating that a group of stars
was physically associated at its time of formation is challenging.
While some young groups show kinematic evidence for expansion
\citep{kuhn_kinematics_2019}, many, including Sco-Cen, do not
\citep{wright_kinematics_2018}.  This complicates the feasibility of
deriving kinematic ages through traceback, as
well as through the expansion itself
\citep[see][]{crundall_chronostar_2019}.  
A more minimal approach is
that suggested by \citet{tofflemire_2021}: search for coeval,
phase-space neighbors, measure their ages, and determine if they share
a common age.  This approach can demonstrate whether a star is {\it
currently associated} with a set of coeval stars, which is much easier
than determining what the association looked like in the past.  Our
analysis of CH-2 meets the latter standard for the existence of a
$\approx$40\,Myr assocation today.  It would be a worthy exercise for
future work to perform a similar search for coeval phase-space
neighbors on the entire dataset of known exoplanet hosts.  For the
time being, we can offer the anecdotal point that in our experience,
most stars do not have dozens of 40\,Myr neighbors within a
local volume of a few \kms\ and tens of parsecs.

@@

\paragraph{Cep-Her}
Our analysis to date has focused only on portions of Cep-Her that were
observed by Kepler: RSG-5, CH-2, and the $\delta$~Lyr cluster.  The
membership and kinematics of the other subgroups shown in
Figure~\ref{fig:XYZvtang} deserve independent attention.  R.~Kerr and
collaborators have {\bf acquired N spectra} from which radial
velocities will be derived in their upcoming study.
One important aspect of these analyses will be to assess whether the 
traceback approach could be applicable.
However if the
estimate that Cep-Her has $\gtrsim$3{,}500 stars is correct then more
data might be required to fully untangle the kinematics of the various
groups.  Wide-field spectroscopic surveys such as LAMOST
\citep{zhao_2012_LAMOST} or SDSS-V \citep{kollmeier_2017} could
enable such analyses, while also
providing sensitivity to the Li 6708\,\AA\ line.  Gaia
DR3 may also provide RVS spectra for some of the brighter F and G
dwarfs, which would contain the calcium infrared triplet as another
age indicator.

A number of worthy photometric projects also seem possible given the
new understanding of the complex.  One is asteroseismology of the
$\delta$~Sct stars, using either TESS or Kepler data
\citep{bedding_very_2020}.  For cases in which the modes are resolved,
this might yield age estimates for the subgroups independent of other
approaches.  Other projects could include searches of the Kepler light
curves for exocomets \citep{zieba_transiting_2019}, and for missed
planets around the most rapid rotators.

@@

\paragraph{Table~2} contains candidate Cep-Her members with weights $\alpha>0.02$
observed by Kepler.  More restrictive weight cuts
would be needed if one wanted to remove the majority of field star interlopers: at
least half of the stars included in the table are unlikely
to be bonafide members of Cep-Her.  Table~2  was created by
cross-matching candidate Cep-Her members (selected using Gaia EDR3;
Section~\ref{subsec:members}) against a Kepler to Gaia DR2 cross-match
(the \texttt{gaia-kepler.fun} crossmatch database created by Megan
Bedell).  The \texttt{kic\_dr2\_ang\_dist} column is from the latter
table.  The EDR3 to DR2 match was performed using the
\texttt{gaiaedr3.dr2\_neighbourhood} table, and the closest proper
motion and epoch-corrected angular distance neighbor was taken as the
single best match.  The \texttt{edr3\_dr2\_mag\_diff} column
gives some indication of the reliability of this EDR3 to DR2
conversion, as there are a few cases between Gaia DR2 and EDR3 where
partially resolved binaries became fully resolved.

>>>>

Color-absolute magnitude diagrams (CAMDs) of the candidate RSG-5 and
CH-2 members are shown in the upper row of Figure~\ref{fig:age}.  The
stars from the $\delta$~Lyr cluster are from
\citet{bouma_kep1627_2022}, and the field stars are from the Gaia EDR3
Catalog of Nearby Stars \citep{gaia_gcns_2021}.  To make these
diagrams, we imposed the data filtering criteria from
\citet[][Appendix B]{GaiaCollaboration2018}, which include binaries
while omitting instrumental artifacts from for instance low
photometric signal to noise, or a small number of visibility periods.
We then corrected for extinction using the
\citet{lallement_threedimensional_2018} dust
maps and the extinction
coefficients $k_X\equiv A_X/A_0$ from \citet{GaiaCollaboration2018},
assuming that $A_0 = 3.1 E(B-V)$.  This yielded a mean and standard
deviation for the reddening of $E(B-V)=0.036\pm0.002$ for RSG-5, and
$E(B-V)=0.017\pm0.001$ for CH-2.  By way of comparison, in
\citet{bouma_kep1627_2022} the same query for the $\delta$~Lyr cluster
yielded $E(B-V)=0.032\pm0.006$.  Finally, for the plots we set the
color range to best visualize the region of maximal age information
content: the pre-main-sequence.

@@

Figure~\ref{fig:age} also shows that most RSG-5 and CH-2 members
overlap with the $\delta$~Lyr cluster, and that the groups are
therefore roughly the same age.  To quantify this, we use the method
introduced by \citet[][their Section~6.3]{gagne_mutau_2020}.  The idea
is to fit the pre-main-sequence loci of a set of reference clusters,
and to then model the locus of the target cluster as a linear
combination of these reference cluster loci.  For our reference
clusters, we used UCL, IC\,2602, and the Pleiades, with the
memberships reported by \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively.  We adopted ages of 16\,Myr for
UCL \citep{pecaut_star_2016}, 38\,Myr for IC\,2602
\citep{david_ages_2015,randich_gaiaeso_2018}
%\footnote{ Ages for
%IC\,2602 vary from 40 to 46\,Myr based on lithium-depletion-boundary
%(LDB) measurements \citep{dobbie_ic_2010,randich_gaiaeso_2018}, and
%from 30 to 46\,Myr based on isochronal analyses
%\citep{stauffer_rotational_1997,david_ages_2015,bossini_age_2019}.},
and 112\,Myr for the Pleiades \citep{dahm_2015}.  These assumptions
and the subsequent processing steps taken to exclude field stars and
binaries were identical to those described in
\citet{bouma_kep1627_2022}.  The mean and uncertainty of the resulting
age posterior are $46^{+9}_{-7}$\,Myr for RSG-5, and
$36^{+10}_{-8}$\,Myr for CH-2.  For comparison, this procedure yields
an age for the $\delta$~Lyr cluster of $38^{+6}_{-5}$\,Myr.  The
slightly older isochronal age of RSG-5 is consistent with its location
relative to the $\delta$~Lyr cluster in the upper left panel of
Figure~\ref{fig:age}.

@@

We selected stars suitable for gyrochronology by requiring $\bpmrpo
\geq 0.5$ to focus on FGKM stars that experience magnetic braking.
For TESS, we also restricted our sample to $G<16$, to ensure the stars
are bright enough to extract usable light curves from the full-frame
images.  The magnitude cut corresponds to $\bpmrpo < 2.6$
($\sim$M3V) at the relevant distances.  These cuts gave 19 stars in
CH-2 and 47 stars in RSG-5.  We extracted light curves from the TESS
images using the \texttt{unpopular} package \citep{hattorio_2021_cpm},
and regressed them against systematics with its causal pixel model.
We measured rotation periods using Lomb-Scargle periodograms and
visually vetted the results using an interactive program that allows
us to switch between TESS Cycles, select particular sectors, flag
stars with multiple periods, and correct half-period harmonics. For
ZTF, we used the same color cut to focus on FGKM stars, but restricted
the sample to $13 < G < 18$ to avoid the saturation limit on the
bright end and ensure sufficient photometric precision at the faint
end. We followed the procedure outlined in \citet{curtis_rup147_2020}:
we downloaded $8'\times8'$ image cutouts, ran aperture photometry for
the target and neighboring stars identified with Gaia, and used them
to define a systematics correction to refine the target light curves.

The lower panels of Figure~\ref{fig:age} show the results.  In RSG-5,
41/47 stars have rotation periods faster than the Pleiades (87\%).
This numerator omits the two stars with periods $>$$12$\,days visible
in the lower-left panel of Figure~\ref{fig:age}.  The age
interpretation for these latter stars, particularly the $\approx$M2.5
dwarf, is not obvious.  \citet{rebull_usco_2018} for instance have
found numerous M-dwarfs with 10-12 day rotation periods at ages of
USco ($\sim$$8$\,Myr), and some may still exist at ages of LCC
($\sim$$16$\,Myr; L.~Rebull in preparation).  Regardless, given that
nearly no field star outliers seem to be present on the RSG-5 CAMD,
the fact that we do not detect rotation periods for $\approx$13\% of
stars should perhaps be taken as an indication for the fraction of
stars for which rotation periods might not be detectable, due to
{e.g.}, pole-on stars having lower amplitude starspot modulation.

@@

A few salient properties of the Kepler objects in Cep-Her can be
gleaned from Figure~\ref{fig:age}.  The stars span spectral types of
G8V (Kepler-1627) to K6V (KOI-7913 A).  The secondary in the KOI-7913
system has spectral type $\approx$K8V.  And given that a star with
Solar mass and metallicity arrives at the zero-age main sequence at
$t\approx40$ Myr \citep{choi_mesa_2016}, these stars are all in the
late stages of their pre-main-sequence contraction.

@@

We fitted the data as follows.  Given the transit
ephemeris from \citet{thompson_planetary_2018}, we first trimmed the
light curve to a local window around each transit that spanned three
transit durations before and after each mid-transit time.  The
out-of-transit points in each local window were then fitted with a
fourth-order polynomial, which was divided out from the light curve.
The resulting flattened transits were then fitted with a transit model
that assumed quadratic limb darkening.  The model therefore included 8
free parameters for the transit ($\{P, t_0, \log R_{\rm p}/R_\star, b,
u_1 ,u_2, R_\star, \log g\}$), 2 free parameters for the light curve
normalization and a white noise jitter ($\{\langle f \rangle, \sigma_f
\}$), and 5 fixed parameters for each transit.

@@

A potential drawback of our approach is that to remove
the starspot-induced variability, we fixed 5 
parameters per transit to their MAP values.
An alternative could be to fit the
planetary transits simultaneously with the starspot-induced
variability using a quasiperiodic Gaussian process (GP).  We explored
this approach, but found that it sometimes required fine-tuning of the
hyperparameter priors, otherwise the GP would overfit flares,
instrumental noise, and any other variability that was not part of the
transit.  This failure mode is pernicious, in that it yields an
ill-founded sense of confidence in a visually clean fit.  Our model is
simpler, and it has the benefit that the white noise jitter never
trades off with any parameter equivalent to a damping timescale for
the coherence of the GP.  It is also computationally efficient, and it
captures the planetary parameters about which we care the most.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
    Planets younger than a gigayear with ages more precise than a
    factor of three are emphasized. The Cep-Her planets are
    Kepler-1643~b ($\square$), KOI-7368~b ($\triangledown$),
    KOI-7913~Ab (X), and Kepler-1627~Ab (+).  Interesting trends in
    the population of young planets currently include {\it i)} their
    large sizes and {\it ii)} the lack of young hot Jupiters.  The new
    objects of interest in Cep-Her have normal mini-Neptune sizes
    between 2 and 3\,$R_\oplus$, which is a novelty given their ages.
    Parameters are from the NASA Exoplanet Archive (2022 Apr 5).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

The most significant novelty about Kepler-1643~b, KOI-7368.01, and
KOI-7913~Ab is that their sizes are normal, relative to the known
population of gigayear-old mini-Neptunes.  At field star ages,
mini-Neptune sizes span 1.8\,$R_\oplus$ to 3.6\,$R_\oplus$, with the
most common size being $\approx 2.4\,R_\oplus$
\citep[][Figure~7]{Fulton_et_al_2017}.  The known planets younger than
$10^8$ years are almost all larger, with sizes between 4 and
10$\,R_\oplus$
\citep{Mann_K2_33b_2016,David_et_al_2016,benatti_possibly_2019,david_four_2019,newton_tess_2019,rizzuto_tess_2020,bouma_cluster_2020,mann_toi1227_2022}.
Figure~\ref{fig:rp_period_age} explores this in more detail by showing
the sizes, orbital periods, and ages of the known transiting planets,
emphasizing planets with precise ages.  The smallest previously known
planets comparable to the new Cep-Her mini-Neptunes are AU~Mic~c
($3.0\pm0.2\,R_\oplus$, see \citealt{martioli_aumicbc_2021} and
\citealt{gilbert_flares_2022}), Kepler-1627~Ab ($3.8\pm0.2\,R_\oplus$;
\citealt{bouma_kep1627_2022}), and AU~Mic~d ($4.2\pm0.2\,R_\oplus$;
\citealt{plavchan_planet_2020}).

The theoretical expectation is that mini-Neptunes with sizes of 2 to
3\,$R_\oplus$ should be common at ages of $10^7$ to $10^8$ years.
This expectation is tied to inferences about the initial distributions
of planetary core mass, core composition, and atmospheric mass
fraction \citep{owen_evaporation_2017}.  The Kelvin-Helmholtz cooling
timescale, which is tied to the entropy of the planetary interior once
the disk disperses, could also play a significant role
\citep{owen_constraining_2020}.  As an example,
\citet{rogers_unveiling_2021} predicted that given a core-mass
distribution peaked at $\approx$$4$\,$M_\oplus$, an ice-poor rock/iron
core composition, and a typical H/He mass fraction of $\approx$4\%,
there should be a maximum in planet occurrence at 2 to 3\,$R_\oplus$
at times between 10 and 100\,Myr.  The models
advanced by \citet{gupta_signatures_2020} and
\citet{lee_primordial_2021} agree; their differences lie in the mechanism
for producing the radius valley.  If the radius valley is
primordial and created by gas accretion physics, then super-Earths
($<$$1.8$\,$R_\oplus$) would be common as early as $10^7$ years
\citep{lee_primordial_2021}.   The photoevaporation-driven models more
often quote $10^8$ year timescales for production of
atmosphere-stripped super-Earths, while the models with the mass-loss
driven by a slow escape of heat from the core predict longer
$\sim$$10^9$ year timescales (but see \citealt{king_2021}).

@@

To quantify the density difference between CH-2 and RSG-5, we can
compare the spatial and velocity volumes searched for each group.  For
RSG-5, we drew \nrsgfive\ candidate members from a $30\,{\rm
pc}\times30\,{\rm pc}\times40\,{\rm pc}$ rectangular prism, given a
$1.5 {\rm \mkms} \times 2.5 {\rm \mkms }$ rectangle in apparent
galactic velocity.  For CH-2, our \nchtwo\ candidate members came from
a rectangular prism of dimension $50\,{\rm pc}\times40\,{\rm
pc}\times30\,{\rm pc}$, and a rectangular box of $2 {\rm \mkms} \times
4 {\rm \mkms}$.  If we define the searched volume in units of ${\rm
pc}^3\,{\rm km^2}\,{\rm s^{-2}}$, then the volume ratio of CH-2 to
RSG-5 is 3.5 to 1.  The ratio of number densities (candidate members
per unit searched volume) in RSG-5 relative to CH-2 is 16 to 1.

Given its low density, in CH-2 really a star cluster?  For this
discussion, we adopt the definition that a star cluster is a group of
at least 12 stars that was physically associated at its time of
formation.  The ``12'' is set to distinguish star clusters from
high-order multiples \citep[see][]{krumholz_star_2019}.  Dissolved
clusters and their tidal tails are therefore included in our concept
of clusters.  We do not however require a threshold number of stars
per unit spatial volume for a group to be a ``cluster''.  The latter
point acknowledges that an important factor in cluster identification
is also the density in velocity space.  Perhaps once stellar rotation
periods and chemical abundances reach the same level of ubiquity as
stellar proper motions, they might enable further refinement of our
ability to discover stars that formed together.

From a data-driven perspective, demonstrating that a group of stars
was physically associated at its time of formation is challenging.
While some young groups show kinematic evidence for expansion
\citep{kuhn_kinematics_2019}, many, including Sco-Cen, do not
\citep{wright_kinematics_2018}.  This complicates the feasibility of
deriving kinematic ages through traceback, as well as through the
expansion itself \citep[see][]{crundall_chronostar_2019}.  A more
minimal approach is that suggested by \citet{tofflemire_2021}: search
for coeval, phase-space neighbors, measure their ages, and determine
if they share a common age.  This approach can demonstrate whether a
star is currently associated with a set of coeval stars, which
is much easier than determining what the association looked like in
the past.  Our analysis of CH-2 meets the latter standard for the
existence of a $\approx$40\,Myr assocation.  It would be a worthy
exercise for future work to perform a similar search for coeval
phase-space neighbors on the entire dataset of known exoplanet hosts.
For the time being, we can offer the anecdotal point that in our
experience, most stars do not have dozens of 40\,Myr neighbors within
a local volume of a few \kms\ and tens of parsecs.

@@

\paragraph{Cep-Her}
Our analysis to date has focused only on portions of Cep-Her that were
observed by Kepler: RSG-5, CH-2, and the $\delta$~Lyr cluster.  In
\citet{bouma_kep1627_2022} as well as this work, we have shown that
these groups share similar ages, and have kinematic correlations that
suggest a common origin.  With that said, the membership and
kinematics of the other subgroups shown in Figure~\ref{fig:XYZvtang}
deserve independent attention.  An important aspect of the work that
remains will be to acquire radial velocities of a large subset of the
stars, to assess whether the traceback approach could be applicable.
Wide-field spectroscopic surveys such as LAMOST
\citep{zhao_2012_LAMOST} or SDSS-V \citep{kollmeier_2017} could enable
such analyses, while also providing sensitivity to the Li 6708\,\AA\
line.  Gaia DR3 may also provide RVS spectra for the brighter F and G
dwarfs; these would contain the calcium infrared triplet as another
age indicator.  These indicators, combined with better kinematics,
will be needed to definitively unravel the formation history of the
complex.

A number of worthy photometric projects also seem possible given the
new understanding of Cep-Her.  One is asteroseismology of the
$\delta$~Sct stars, using either TESS or Kepler data
\citep{bedding_very_2020}.  For cases in which the modes are resolved,
this might yield age or metallicity estimates for the subgroups
independent of other approaches.  Other projects could include
searches of the Kepler light curves for exocomets
\citep{zieba_transiting_2019}, and for missed planets around the most
rapid rotators.

@@

\paragraph{Table~2} contains candidate Cep-Her members with weights
$\alpha>0.02$ observed by Kepler.  More restrictive weight cuts would
be needed if one wanted to remove the majority of field star
interlopers; at least half of the stars included in the table are
unlikely to be bonafide Cep-Her members.  Table~2  was created by
cross-matching candidate Cep-Her members (selected using Gaia EDR3;
Section~\ref{subsec:members}) against a Kepler to Gaia DR2 cross-match
(the \texttt{gaia-kepler.fun} crossmatch database created by Megan
Bedell).  The \texttt{kic\_dr2\_ang\_dist} column is from the latter
table.  The EDR3 to DR2 match was performed using the
\texttt{gaiaedr3.dr2\_neighbourhood} table, and the closest proper
motion and epoch-corrected angular distance neighbor was taken as the
single best match.  The \texttt{edr3\_dr2\_mag\_diff} column gives
some indication of the reliability of this EDR3 to DR2 conversion, as
there are a few cases between Gaia DR2 and EDR3 where partially
resolved binaries became fully resolved.

\paragraph{Table~3} contains spatial, kinematic, astrometric, and
rotation period information for the \nrsgfive\ candidate RSG-5 members
and \nchtwo\ candidate CH-2 members described in
Section~\ref{subsec:members}.  These are the data used to make the
lower panels of Figure~\ref{fig:age}. 
% Table~3 includes rotation periods for 53 stars with ZTF and 51 stars
% with TESS, for a total of 71 periods reported for unique stars and 32
% overlapping between the surveys.
We adopted the ZTF period over the
TESS period in three cases: (1) Gaia EDR3 2081755809272821248: the
Lomb-Scargle periodogram favored 6.67 days, consistent with the ZTF
period of 6.61 days; however, we flagged it as a candidate
double-dipper, which appears to have inaccurately doubled the TESS
period to 13.34 days; (2) Gaia EDR3 2081737529891330560: we found 3.06
days with TESS and 6.64 days with ZTF; we suspect that TESS captured
the 1/2-period harmonic and adopt the approximately double value from
ZTF; (3) 2134851775526125696: for this star, we measured 1.91 days
with TESS from Cycle 2, but noted that the signal appeared to be
missing in Cycle 4; ZTF found a strong signal at 12.23 days and we
adopt this as the star's period. In the remaining overlap cases, we
adopted the average between TESS and ZTF as the final period. For
these overlap stars, the median absolute deviation is 0.01 days,
showing remarkable consistency between the surveys. For three stars,
we failed to detect a period in TESS but recovered one from ZTF; in
all cases the periods appear to be 13--16 days.  These stars were: (1)
Gaia EDR3 2129930258400157440, for which TESS showed a flat light
curve while ZTF yielded a 15.3-day period; (2) Gaia EDR3
2082376861542398336, LS found a 7.6-day period which we rejected
during visual validation; we found 15.4 days with ZTF, and we suspect
that the weak/rejected signal form TESS might have been a 1/2 period
harmonic; (3) Gaia EDR3 2082397099429013120, similar to the previous
case, we rejected a 6.7-day signal from TESS and recovered a 12.8-day
period with ZTF.
